SubsidyExplorer - Step 3: Classify vessels into management regimes

### 2020-04-09 scripts/01_data_wrangling.Rmd
finished redoing vessel list

title: "SubsidyExplorer - Step 0: Data Wrangling"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

@@

**Subsidy Data**
Estimates of annual fisheries subsidies provision by state from Sumaila et al. (2019) in 2018 US\$. These data were provided to us directly by the authors as a .xlsx file and are stored at `r sumaila_subsidies_path`.
> Sumaila, U. R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H. S., … Pauly, D. (2019). Updated estimates and analysis of global fisheries subsidies. Marine Policy, 109, 103695. https://doi.org/10.1016/j.marpol.2019.103695

Estimates of fisheries support provision by state from the OECD (2008 - 2018). These data were last downloaded from the OECD iLibrary portal as a CSV file on March 10, 2019 and are stored as `r oecd_fse_path`.
> OECD (2019), "Fisheries: Fisheries support estimates", OECD Agriculture Statistics (database), https://doi.org/10.1787/ade64fdc-en (accessed on 10 March 2019).

**Demographic Data**
Total GDP, GDP from fisheries, forestry, and agriculture, and population by state from the World Bank's World Development Indicators Database (2000 - 2018). These data were accessed through the `WDI` package. The code used to pull the data is below. 
> The World Bank (2019). "World Development Indicators", https://datacatalog.worldbank.org/dataset/world-development-indicators (accessed on 24 October 2019).

@@

**Fisheries Data**
Fisheries landings in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al. (2017). These data were were wrangled in the previous script, and the edited data are stored as `r catch_dat_path`. 
> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-capture-production/en (accessed on 24 October 2019).

@@

Fisheries performance indicators
> Anderson, J. L., Anderson, C. M., Chu, J., Meredith, J., Asche, F., Sylvia, G., Smith, M. D., Anggraeni, D., Arthur, R., Guttormsen, A., McCluney, J. K., Ward, T., Akpalu, W., Eggert, H., Flores, J., Freeman, M. A., Holland, D. S., Knapp, G., Kobayashi, M., … Valderrama, D. (2015). The Fishery Performance Indicators: A Management Tool for Triple Bottom Line Outcomes. PLOS ONE, 10(5), e0122809. https://doi.org/10.1371/journal.pone.0122809

**Other**
IUU Consolidated vessel list
> NEED

@@

# Note: Political entities, dependencies, and naming

@@

# FAO Area lookup
fao_area_lookup <- read_csv(paste0(fao_production_path, "CL_FI_WATERAREA_GROUPS.csv")) %>%
  clean_names(case = "snake") %>%
  mutate(keep = ifelse(is.na(fa_region_group), F, T)) %>%
  dplyr::filter(keep) %>%
  dplyr::select(area = code) %>%
  mutate(area = as.integer(area))

@@

# Look at NAs - 8498 entries
combine_nas <- combine_catch_price_dat %>%
  dplyr::filter(is.na(exvessel_inclusive))

@@

This second is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.

>>>>

title: "SubsidyExplorer - Step 1: Data Wrangling"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

@@

**Fisheries (Subsidy) Data**
Estimates of annual fisheries subsidies provision by state from Sumaila et al. (2019) in 2018 US\$. These data were provided to us directly by the authors as a .xlsx file and are stored at `r sumaila_subsidies_path`.
> Sumaila, U. R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H. S., … Pauly, D. (2019). Updated estimates and analysis of global fisheries subsidies. Marine Policy, 109, 103695. https://doi.org/10.1016/j.marpol.2019.103695

Estimates of fisheries support provision by state from the OECD (2008 - 2018). These data were last downloaded from the OECD iLibrary portal as a CSV file on March 10, 2019 and are stored as `r oecd_fse_path`.
> OECD. (2019). Fisheries: Fisheries support estimates. Fisheries and Aquaculture Statistics, OECD Agriculture Statistics (Database). https://doi.org/10.1787/ade64fdc-en

**Demographic Data**
Total GDP, GDP from fisheries, forestry, and agriculture, and population by state from the World Bank's World Development Indicators Database (2000 - 2018). These data were accessed through the `WDI` package. The code used to pull the data is below. 
> World Bank. (2020). World Development Indicators. https://data.worldbank.org/

@@

**Other Fisheries Data**
Fisheries landings in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al. (2017). These data were were wrangled in the previous script, and the edited data are stored as `r catch_dat_path`. 
> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-capture-production/en (accessed on 24 October 2019).

@@

IUU Consolidated vessel list
> NEED

@@

# Note: Country naming, political entities, and dependencies

@@

# FAO Area lookup
fao_area_lookup <- read_csv(paste0(fao_production_path, "CL_FI_WATERAREA_GROUPS.csv")) %>%
  clean_names(case = "snake") %>%
  dplyr::select(area = code) %>%
  mutate(area = as.integer(area))

@@

# Look at NAs - 9398 entries
combine_nas <- combine_catch_price_dat %>%
  dplyr::filter(is.na(exvessel_inclusive))

@@

This section is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.

### 2020-04-09 scripts/02_vessel_list.Rmd
finished redoing vessel list

# Path to cleaned subsidies data file (2018)
subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")

@@

# Directories for the output files generated by this script
results_dir <- here::here("results", "02-vessel-list/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

```{r}
# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
  dplyr::select(flag_iso3 = iso3, flag_sovereign_iso3 = sovereign_iso3, is_EU)

# EU countries
# eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
# 
# # Dutch overseas territories 
# dutch_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
# 
# # French overseas territories 
# french_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
# 
# # Danish overseas territories
# danish_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
# 
# # UK overseas territories
# uk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
# 
# # EU overseas territories
# eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
# 
# # US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
# us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
# 
# # Norwegian overseas territories: 
# norwegian_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]

# 
```

@@

```{r}
# Now lets add sovereign flags
vessel_list <- vessel_list %>%
  left_join(country_dependencies, by = c("flag_iso3" = "flag_iso3"))
```

@@

Before we allocate catches and subsidies, we need to get total fishing kWh by flag and FAO region, as well as by flag.

```{r}
# Effort by flag and fao
effort_flag_fao <- vessel_list %>%
  group_by(flag_iso3, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  ungroup()

@@

catch_flag <- catch_flag_fao %>%
  group_by(iso3) %>%
  summarize(capture_production = sum(capture_production, na.rm = T)) %>%
  ungroup()

@@

revenue_flag <- revenue_flag_fao %>%
  group_by(iso3) %>%
  summarize(landed_value = sum(capture_production, na.rm = T)) %>%
  ungroup()

@@

```{r}
# effort_flag
effort_no_matching_catches <- effort_flag %>%
  dplyr::filter(!(flag %in% catch_flag$iso3))

# There are 3 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag). We're going to try assigning them based on the EEZ in which they spend the most time fishing instead. 
vessels_new_flag <- vessel_list %>%
  dplyr::filter(flag %in% effort_no_matching_catches$flag) %>% # 773 entries 
  dplyr::filter(eez_id != 0) %>% # remove high seas entries
  group_by(ssvid) %>%
  top_n(1, fishing_KWh_eez_fao) %>%
  summarize(new_flag = unique(territory1_iso3))  #486 vessels

# So  there are 75 vessels that have no flag and that only fish on the high seas... We'll be excluding those vessels
vessel_info_new_flag <- vessel_list %>%
  dplyr::filter(ssvid %in% vessels_new_flag$ssvid) %>%
  left_join(vessels_new_flag, by = "ssvid") %>%
  mutate(flag = new_flag) %>%
  dplyr::select(-new_flag) # 688 entries

# Fix vessel list 
vessel_list <- vessel_list %>%
  dplyr::filter(!(flag %in% effort_no_matching_catches$flag)) %>%
  bind_rows(vessel_info_new_flag) %>%
  dplyr::filter(!is.na(flag))
vessel_list$flag[vessel_list$flag == "ESH"] <- "MAR"
vessel_list$flag[vessel_list$flag == "CPT"] <- "FRA"
```

Turns out they all do!

```{r}
# And we redo one last time
effort_flag_fao <- vessel_list %>%
  group_by(flag, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
  ungroup()

# Effort by flag
effort_flag <- effort_flag_fao %>%
  group_by(flag) %>%
  summarize(fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup()

# effort_flag
effort_no_matching_catches <- effort_flag %>%
  dplyr::filter(!(flag %in% catch_flag$iso3))
```

@@

```{r}
# Let's get region specific catch rates we can use for when we don't have matching flag/fao pairs
catch_region_no_match <- catch_flag_fao %>%
  anti_join(effort_flag_fao, by = c("iso3" = "flag", "area" = "fao_region")) %>%
  mutate(join_region = case_when(area == 88 ~ 58,
                                      TRUE ~ area)) %>%
  group_by(join_region) %>%
  summarize(tot_landings = sum(landings, na.rm = T),
            tot_revenue = sum(revenue, na.rm = T))

# Get matching catch/effort flag and fao region pairings
match_effort_catch <- effort_flag_fao %>%
  left_join(catch_flag_fao, by = c("flag" = "iso3", "fao_region" = "area")) %>%
  arrange(flag, fao_region) %>%
  mutate(is_match = ifelse(!is.na(fishing_KWh) & !is.na(landings), T, F))

# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
match <- match_effort_catch %>%
  dplyr::filter(is_match) %>%
  mutate(catch_per_fishing_KWh = landings/fishing_KWh,
         revenue_per_fishing_KWh = revenue/fishing_KWh) %>%
  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)

# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
no_match <- match_effort_catch %>%
  dplyr::filter(is_match == F)

# Get leftover rates
rates_no_match <- no_match %>%
  mutate(join_region = case_when(fao_region == 18 ~ 21,
                                 fao_region == 67 ~ 77,
                                 fao_region == 47 ~ 41,
                                 TRUE ~ fao_region)) %>%
  full_join(catch_region_no_match, by = c("join_region")) %>%
  group_by(join_region) %>%
  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T),
         catch_per_fishing_KWh = tot_landings/tot_fishing_KWh,
         revenue_per_fishing_KWh = tot_revenue/tot_fishing_KWh) %>%
  ungroup() %>%
  group_by(fao_region) %>%
  summarize(catch_per_fishing_KWh = unique(catch_per_fishing_KWh),
            revenue_per_fishing_KWh = unique(revenue_per_fishing_KWh))

# Add back in to our flag/fao pairings
no_match <- no_match %>%
  left_join(rates_no_match, by = c("fao_region")) %>%
  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)

# Combine
catch_rates_flag_fao_all <- match %>%
  bind_rows(no_match)
```

@@

```{r}
vessel_list <- vessel_list %>%
  left_join(catch_rates_flag_fao_all, by = c("flag", "fao_region"))
```

@@

```{r}
# Load subsidy data
subsidies_dat <- read_csv(subsidy_dat_path) %>%
  dplyr::filter(year == 2018)

@@

# Resummarize effort including overseas territories with their sovereign
effort_flag_revised <- effort_flag %>%
  mutate(flag_for_matching = case_when(flag %in% c("USA", us_territories) ~ "USA",
                              flag %in% c("FRA", french_territories) ~ "FRA",
                              flag %in% c("GBR", uk_territories) ~ "GBR",
                              flag %in% c("NOR", norwegian_territories) ~ "NOR",
                              flag %in% c("DNK", danish_territories) ~ "DNK",
                              flag %in% c("NLD", dutch_territories) ~ "NLD",
                              TRUE ~ flag)) %>%
  group_by(flag_for_matching) %>%
  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T))

# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_flag_revised %>%
  left_join(subsidies_flag, by = c("flag_for_matching" = "iso3")) %>%
  group_by(flag) %>%
  summarize_at(subsidy_types, list(per_fishing_KWh = ~./tot_fishing_KWh))
subsidy_rates_flag[is.na(subsidy_rates_flag)] <- 0

# Join back to vessel_list
vessel_list <- vessel_list %>%
  left_join(subsidy_rates_flag, by = c("flag"))

@@

vessel_list <- vessel_list %>%
  mutate(catch = fishing_KWh_eez_fao*catch_per_fishing_KWh,
         revenue = fishing_KWh_eez_fao*revenue_per_fishing_KWh) %>%
  mutate_at(paste0(subsidy_types, "_per_fishing_KWh"), list(subs = ~.*fishing_KWh_eez_fao)) %>%
  rename_at(paste0(subsidy_types, "_per_fishing_KWh_subs"), rename_me) %>%
  dplyr::select_at(vars(-contains("_per_fishing_KWh"))) %>%
  mutate(good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))))

write_csv(vessel_list, paste0(results_dir, "vessel-list-2018-raw.csv"))
```

>>>>

# Path to cleaned subsidies data file (2018)
subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")
subsidy_year <- 2018

@@

# Directories for the output files generated by this script
results_dir <- here::here("results", "02-vessel-list/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

# Do you wnat to make figures? 
make_figures <- FALSE
```

@@

```{r}
# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
  dplyr::select(flag_iso3 = iso3, flag_sovereign_iso3 = sovereign_iso3, is_EU, is_dependency = is_overseas_territory)

@@

@@

Before we allocate catches and subsidies, we need to get total fishing kWh by flag and FAO region, as well as by flag. 
```{r}
# Effort by flag and fao
effort_flag_fao <- vessel_list %>%
  group_by(flag_iso3, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  ungroup()

@@

@@

# Combine catches and revenues
catch_revenue_flag_fao <- catch_flag_fao %>%
  left_join(revenue_flag_fao, by = c("iso3", "fao_region")) %>%
  mutate(fao_region = as.character(fao_region))

catch_revenue_flag <- catch_revenue_flag_fao %>%
  group_by(iso3) %>%
  summarize(capture_production = sum(capture_production, na.rm = T),
            landed_value = sum(landed_value, na.rm = T))

@@

```{r}
# Fishing effort (flag) for which we don't have matching catch data - 2 states (Christmas Island and NA)
effort_no_matching_catches <- effort_flag %>%
  anti_join(catch_revenue_flag, by = c("flag_iso3" = "iso3"))

catch_no_matching_effort <- catch_revenue_flag %>%
  anti_join(effort_flag, by = c("iso3" = "flag_iso3"))

# There are 2 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag). We're going to try assigning them based on the EEZ in which they spend the most time fishing instead. 
vessels_no_catches <- vessel_list %>%
  dplyr::filter(flag_iso3 %in% effort_no_matching_catches$flag_iso3) %>% # 1094 entries 
  group_by(ssvid, eez_id, eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3) %>%
  summarize(fishing_KWh_eez_fao_ter = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  group_by(ssvid) %>%
  mutate(rank = dense_rank(desc(fishing_KWh_eez_fao_ter)),
         max_rank_no_hs = min(rank[!is.na(eez_territory1_iso3)])) %>%
  ungroup()

# Isolate vessels for which we can assign a new flag this way: 474 vessels. 
vessels_new_flag <- vessels_no_catches %>%
  dplyr::filter(max_rank_no_hs != Inf) %>%
  group_by(ssvid) %>%
  summarize(new_flag = eez_territory1_iso3[rank == max_rank_no_hs])

# Vessels still missing flag: So there are 75 vessels that have no flag and that only fish on the high seas... We'll be excluding those vessels. 
vessels_missing_flag <- vessels_no_catches %>%
  dplyr::filter(max_rank_no_hs == Inf)

# Assign new flags to those vessels and remove those missing a flag state.  
vessel_list <- vessel_list %>%
  dplyr::filter(!(ssvid %in% vessels_missing_flag$ssvid)) %>%
  left_join(vessels_new_flag, by = "ssvid") %>%
  mutate(flag_iso3 = case_when(!is.na(new_flag) ~ new_flag,
                          TRUE ~ flag_iso3)) %>%
  dplyr::select(-new_flag)

```{r}
# Now lets add sovereign flags
vessel_list <- vessel_list %>%
  left_join(country_dependencies, by = c("flag_iso3" = "flag_iso3"))

# And manually correct two - Clipperton Atoll and Western Sahara
vessel_list$flag_iso3[vessel_list$flag_iso3 == "CPT"] <- "FRA"
vessel_list$flag_iso3[vessel_list$flag_iso3 == "ESH"] <- "MAR"
```

Now they all do and we can assign catches.

```{r}
# And we redo one last time
effort_flag_fao <- vessel_list %>%
  group_by(flag_iso3, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  ungroup()

# Effort by flag
effort_flag <- effort_flag_fao %>%
  group_by(flag_iso3) %>%
  summarize(fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup()

# effort_flag
effort_no_matching_catches <- effort_flag %>%
  anti_join(catch_revenue_flag, by = c("flag_iso3" = "iso3"))
```

@@

```{r}
# Get matching catch/effort flag and fao region pairings
effort_catch_flag_region_matching <- effort_flag_fao %>%
  left_join(catch_revenue_flag_fao, by = c("flag_iso3" = "iso3", "fao_region")) %>%
  arrange(flag_iso3, fao_region) %>%
  mutate(is_flag_region_match = ifelse(!is.na(fishing_KWh) & !is.na(capture_production), T, F))

# Matches
flag_region_matches <- effort_catch_region_matching %>%
  dplyr::filter(is_flag_region_match)

# Calculate catch rates for those entries with matching catches and efforts by flag/fao region pairing
rates_flag_region_matches <- flag_region_matches %>%
  mutate(flag_region_catch_per_fishing_KWh = capture_production/fishing_KWh,
         flag_region_revenue_per_fishing_KWh = landed_value/fishing_KWh) %>%
  dplyr::select(flag_iso3, fao_region, flag_region_catch_per_fishing_KWh, flag_region_revenue_per_fishing_KWh)

### -----------------------------------------------------------------
# Get matching catch/effort flag pairings
effort_catch_flag_matching <- effort_flag %>%
  left_join(catch_revenue_flag, by = c("flag_iso3" = "iso3")) %>%
  arrange(flag_iso3) %>%
  mutate(is_flag_match = ifelse(!is.na(fishing_KWh) & !is.na(capture_production), T, F))

### Matches 
flag_matches <- effort_catch_flag_matching %>%
  dplyr::filter(is_flag_match)

# Calculate catch rates for those entries with matching catches and efforts by flag/fao region pairing
rates_flag_matches <- flag_matches %>%
  mutate(flag_catch_per_fishing_KWh = capture_production/fishing_KWh,
         flag_revenue_per_fishing_KWh = landed_value/fishing_KWh) %>%
  dplyr::select(flag_iso3, flag_catch_per_fishing_KWh, flag_revenue_per_fishing_KWh)

### -------------------
comprehensive_catch_rates <- effort_catch_flag_region_matching %>%
  left_join(rates_flag_region_matches, by = c("flag_iso3", "fao_region")) %>%
  left_join(rates_flag_matches, by = c("flag_iso3")) %>%
  mutate(catch_per_fishing_KWh = case_when(!is.na(flag_region_catch_per_fishing_KWh) ~ flag_region_catch_per_fishing_KWh,
                                           TRUE ~ flag_catch_per_fishing_KWh),
         revenue_per_fishing_KWh = case_when(!is.na(flag_region_revenue_per_fishing_KWh) ~ flag_region_revenue_per_fishing_KWh,
                                           TRUE ~ flag_revenue_per_fishing_KWh)) %>%
  dplyr::select(flag_iso3, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)
```

@@

```{r}
vessel_list <- vessel_list %>%
  left_join(comprehensive_catch_rates, by = c("flag_iso3", "fao_region"))
```

@@

```{r}
# Load subsidy data
subsidies_dat <- read_csv(subsidy_dat_sumaila_path) %>%
  dplyr::filter(year == subsidy_year)

@@

# Resummarize effort including overseas territories with their sovereign
effort_sovereign_flag <- vessel_list %>%
  group_by(flag_sovereign_iso3) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
  ungroup()

# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_sovereign_flag %>%
  inner_join(subsidies_flag, by = c("flag_sovereign_iso3" = "iso3")) %>%
  group_by(flag_sovereign_iso3) %>%
  summarize_at(subsidy_types, list(per_fishing_KWh = ~./fishing_KWh))
subsidy_rates_flag[is.na(subsidy_rates_flag)] <- 0

# Join back to vessel_list
vessel_list <- vessel_list %>%
  left_join(subsidy_rates_flag, by = c("flag_sovereign_iso3"))

@@

vessel_list <- vessel_list %>%
  mutate(catch = fishing_KWh_eez_fao_ter*catch_per_fishing_KWh,
         revenue = fishing_KWh_eez_fao_ter*revenue_per_fishing_KWh) %>%
  mutate_at(paste0(subsidy_types, "_per_fishing_KWh"), list(subs = ~.*fishing_KWh_eez_fao_ter)) %>%
  rename_at(paste0(subsidy_types, "_per_fishing_KWh_subs"), rename_me) %>%
  dplyr::select_at(vars(-contains("_per_fishing_KWh"))) %>%
  mutate(good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))))

write_csv(vessel_list, paste0(results_dir, "vessel_list_2018_raw.csv"))
```

### 2020-04-09 scripts/03_management.Rmd
finished redoing vessel list

The purpose of this script is to classify all of our vessels into three different management regimes: 
- Managed
- Intermediate
- Open access

@@

In addition to the vessel list created in the previous script, the following data sources are used to classify management regimes:

@@

# Path to vessel list
vessel_list_path <- here::here("results", "1-vessel-list", "vessel-list-2018-raw.csv")

>>>>

The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into three different management regimes: 
- Well-managed
- Managed
- Open access

@@

@@

# Path to vessel list
vessel_list_path <- here::here("results", "02-vessel-list", "vessel-list-2018-raw.csv")
